Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-12-09 02_Paper/paper.tex
Conclusion

Based on the literature review, we observed that the hundred percent quality check method proves to be the most efficient method to guarantee the final product quality, however, the high implementation cost is its biggest draw-back. On the other hand, we have the statistical methods, which are known to be fast and efficient, but the lack of reviewing each product until the next bach review might imply a considerable loss whenever NOK products are found. This is based on the uncertainty of when did the error occurs and how many products are affected.

By implementing ML models capable to predict the quality of the product, just by the initial conditions of the process would be a great asset for the industrial processes. Within the limits of our work, we predict with 98\% certainty the product quality by implementing a decision tree model with a 6-variables vector as input. 
However, our decision for industrial applications would be the MLP with 88\% accuracy as to guarantee the QC and avoid labeling a NOK piece as OK. For further work, we expect to increase the certainty of the prediction model by collecting more data-samples and experimenting with other, more complex, ML models.

It is important to state that this prediction model is not yet ready to fully replace the statistical methods, not the hundred percent quality check method. However, a combination of SPC along prediction models could work well together, since the prediction model will evaluate each produced piece, and this will somehow compensate one disadvantage the statistical methods have.

>>>>

Based on the explorative literature review, we observed that the hundred percent quality check method proves to be the most efficient method to guarantee the final product quality, however, the high implementation cost is its biggest draw-back. On the other hand, we have the statistical methods, which are known to be fast and efficient, but the lack of reviewing each product until the next bach review might imply a considerable loss of the produced products whenever NOK products are found. This is based on the uncertainty of when did the error occurs and how many products are affected.

By implementing ML models capable to predict the quality of the product, based on just the initial conditions of the process would be a great asset for the industrial processes. Within the limits of our work, we predict with 98\% certainty the product quality by implementing a decision tree model with a 6-variables vector as input. 
However, our decision for industrial applications would be the MLP with 88\% accuracy as to guarantee that all passed parts are OK and avoid labeling a NOK piece as OK. For further work, we expect to increase the accuracy of the prediction model by collecting more data-samples and experimenting with other, more complex, ML models.

It is important to state that this prediction model is not yet ready to fully replace the statistical methods, not the hundred percent quality check method, since this research is still on its early stages and need further development. However, a combination of SPC along prediction models could work well together, since the prediction model will evaluate each produced piece, and this might compensate one disadvantage of the statistical methods.
